---
title: "W_UP_01"
author: "Dorothy Decker"
date: "Summer 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
library(ggplot2)

ggplot(mydata, aes(x = position, y = pushups)) +
  geom_boxplot() +
  labs(x = "Position", y = "Pushups") +
  ggtitle("Box Plot of Pushups by Position") +
  theme(plot.title = element_text(size = 20, hjust = 0.5))




```

According to the plot, if you compare the two box plots, based on position the skill category has higher push ups. By looking at the graph, you can note the skill position is higher on the graph, which equates the higher amount of pushups. The median is higher for the skill position as well. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(pushups~position,data=mydata)
```

According to the numerical results, there is a huge difference between the two positions. Every single number on the skill position is higher than the the line position. For example, by looking at the mean, the mean for the line position 17.12500 while the mean for the skill position is 49.72727. With this said, its clear the skill position do more push ups.  

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(pushups~position,data=mydata)
```
Clearly, the skill players can do a lot more push ups than line players. The original hypothesis is incorrect. According to the data, there is a big difference between the two positions.


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

